|

### 2023-02-05 paper.Rmd
autogit

One major limitation for the experiments conducted during the reseach phase of this thesis has been the large computational effort for experimenting with DAE-GP. Since single runs for DAE-GP have a run-time of many hours, it was not possible for me to extend the experiments to larger population sizes or more generations. Also I did not perform an extended optimization of hyperparameters (e.g by using a grid search strategy) which might yield configurations that increase the benefits of pre-training. As described in subsection [Effect on Run-Time], sampling new solutions has been a large contributor to the large performance hit on run-time by using pre-training. It could be a worthwhile endevour to explore the main factors that increase sampling time for pre-trained DAE-GP to more efficiently exploit the benefits of pre-training like reducing the number of training epochs.

>>>>

One major limitation for the experiments conducted during the reseach phase of this thesis has been the large computational effort for experimenting with DAE-GP. Since single runs for DAE-GP have a run-time of many hours, it was not possible for me to extend the experiments to larger population sizes or more generations. Also I did not perform an extended optimization of hyperparameters (e.g by using a grid search strategy) which might yield configurations that increase the benefits of pre-training. As described in subsection [Influence on Run-Time], sampling new solutions has been a large contributor to the large performance hit on run-time by using pre-training. It could be a worthwhile endevour to explore the main factors that increase sampling time for pre-trained DAE-GP to more efficiently exploit the benefits of pre-training like reducing the number of training epochs.
